### 2023-12-13 supplement.tex
adding plots and more edits to tables

\section{Datasets}

@@

>>>>

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/fashion-mnist-knn-100.png}
    \caption{
        Scaling behavior of algorithms on fashion-mnist with $k=100$. 
    }
    \label{fig:supplement:fashion-mnist-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/sift-knn-100.png}
    \caption{
        Scaling behavior of algorithms on sift with $k=100$. 
    }
    \label{fig:supplement:sift-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/glove-25-knn-100.png}
    \caption{
        Scaling behavior of algorithms on glove-25 with $k=100$. 
    }
    \label{fig:supplement:glove-25-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/random-1000000-128-knn-100.png}
    \caption{
        Scaling behavior of algorithms on random with $k=100$. 
    }
    \label{fig:supplement:random-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/fashion-mnist-indexing.png}
    \caption{
        Indexing time for algorithms on fashion-mnist dataset. 
    }
    \label{fig:supplement:fashion-mnist-indexing}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/glove-25-indexing.png}
    \caption{
        Indexing time for algorithms on glove-25 dataset. 
    }
    \label{fig:supplement:glove-25-indexing}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/sift-indexing.png}
    \caption{
        Indexing time for algorithms on sift dataset. 
    }
    \label{fig:supplement:sift-indexing}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/random-indexing.png}
    \caption{
        Indexing time for algorithms on random dataset. 
    }
    \label{fig:supplement:random-indexing}
\end{figure}
